SubsidyExplorer - Step 6: Run Model

### 2020-09-04 scripts/01_data_wrangling.Rmd
cap fixes

```{r}
# Load data using WDI package'
# wb_demo_dat <- WDI(country = "all",
#                    indicator = c("gdp" = "NY.GDP.MKTP.CD",
#                                  "gdp_ffa" = "NV.AGR.TOTL.CD",
#                                  "population" = "SP.POP.TOTL"),
#                                   start = 2000,
#                                   end = 2018,
#                                   extra = TRUE) %>%
#   dplyr::filter(region != "Aggregates") %>%
#   dplyr::select(iso3 = iso3c,
#                 year,
#                 gdp,
#                 gdp_ffa,
#                 population) %>%
#   mutate(iso3 = as.character(iso3)) %>%
#   arrange(iso3, year) %>%
#   gather(variable, value, c("gdp", "gdp_ffa", "population")) %>%
#   dplyr::filter(!is.na(value)) %>%
#   mutate(units = case_when(variable == "population" ~ "individuals",
#                            TRUE ~ paste0(year, " US$")),
#          source = "World Bank WDI database")
# 
# # Deal with the EU + territories
# wb_dat_eu <- wb_demo_dat %>%
#   dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
#   mutate(entity = "EU") %>%
#   group_by(entity, year, variable, units, source) %>%
#   summarize(value = sum(value, na.rm = T)) %>%
#   rename(iso3 = entity) %>%
#   arrange(iso3, year, variable)
# 
# # Test to make sure there isn't data for any other dependencies - will need to add this once I can figure out why the WDI API isn't working
# wb_dat_overseas_territory <- wb_demo_dat %>%
#   dplyr::filter(iso3 %in% territories$iso3 & !(iso3 %in% eu_territories))
# # Deal with the US + territories
# wb_dat_us <- wb_demo_dat %>%
#   dplyr::filter(iso3 %in% c(us_territories, "USA")) %>%
#   mutate(entity = "USA") %>%
#   group_by(entity, year, variable, units, source) %>%
#   summarize(value = sum(value, na.rm = T)) %>%
#   rename(iso3 = entity) %>%
#   arrange(iso3, year, variable)
# 
# # Add back in
# wb_dat_edit <- wb_demo_dat %>%
#   dplyr::filter(iso3 != "USA") %>%
#   bind_rows(wb_dat_eu) %>%
#   bind_rows(wb_dat_us)
# 
# # Export clean
# write_csv(wb_dat_edit, paste0(data_dir, "world_bank_2020_wdi_tidy.csv"))
# write_csv(wb_dat_edit, paste0(app_data_dir, "world_bank_2020_wdi_tidy.csv"))

# Load in
wb_dat_edit <- read_csv(paste0(data_dir, "world_bank_2020_wdi_tidy.csv"))
```

@@

# Combine 
cap_tier_lookup <- capture_production_lookup %>%
  bind_rows(landed_value_lookup)

>>>>

```{r}
#Load data using WDI package
wb_demo_dat <- WDI(country = "all",
                   indicator = c("gdp" = "NY.GDP.MKTP.CD", # GDP (current US$)
                                 "gdp_ffa" = "NV.AGR.TOTL.CD", # Added value coming from fisheries, forestry, and agriculture (current US$)
                                 "population" = "SP.POP.TOTL", # Total population
                                 "gni_per_capita" = "NY.GNP.PCAP.KD"), # GNI per capita (constant 2010 US$)
                                  start = 2000,
                                  end = 2018,
                                  extra = TRUE) %>%
  dplyr::filter(region != "Aggregates") %>%
  dplyr::select(iso3 = iso3c,
                year,
                gdp,
                gdp_ffa,
                population,
                gni_per_capita) %>%
  mutate(iso3 = as.character(iso3)) %>%
  arrange(iso3, year) %>%
  gather(variable, value, c("gdp", "gdp_ffa", "population", "gni_per_capita")) %>%
  dplyr::filter(!is.na(value)) %>%
  mutate(units = case_when(variable == "population" ~ "individuals",
                           variable == "gni_per_capita" ~ "constant 2010 US$",
                           TRUE ~ paste0(year, " US$")),
         source = "World Bank WDI database")

# # Deal with the EU + territories
wb_dat_eu <- wb_demo_dat %>%
  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
  mutate(entity = "EU") %>%
  group_by(entity, year, variable, units, source) %>%
  summarize(value = sum(value, na.rm = T)) %>%
  rename(iso3 = entity) %>%
  arrange(iso3, year, variable)

# Deal with data for other dependencies
wb_dat_overseas_territories <- wb_demo_dat %>%
  dplyr::filter(iso3 %in% territories$iso3 | iso3 %in% territories$sovereign_iso3) %>%
  left_join(territories, by = c("iso3")) %>%
  mutate(sovereign_iso3 = case_when(is.na(sovereign_iso3) ~ iso3,
                                    TRUE ~ sovereign_iso3)) %>%
  mutate(entity = paste0(sovereign_iso3, "-T")) %>%
  group_by(entity, year, variable, units, source) %>%
  summarize(value = sum(value, na.rm = T)) %>%
  rename(iso3 = entity) %>%
  arrange(iso3, year, variable)

# Add back in
wb_dat_edit <- wb_demo_dat %>%
  bind_rows(wb_dat_eu) %>%
  bind_rows(wb_dat_overseas_territories)

# Export clean
write_csv(wb_dat_edit, paste0(data_dir, "world_bank_2020_wdi_tidy.csv"))
write_csv(wb_dat_edit, paste0(app_data_dir, "world_bank_2020_wdi_tidy.csv"))
```

@@

# Subsidy lookup 
subsidy_totals <- sumaila_2019_dat_edit %>%
  group_by(iso3, year) %>%
  summarize(good_subs = sum(value[type %in% c("A1", "A2", "A3")], na.rm = T),
            bad_subs = sum(value[type %in% c("B1", "B2", "B3", "B4", "B5", "B6", "B7")], na.rm = T),
            ugly_subs = sum(value[type %in% c("C1", "C2", "C3")], na.rm = T)) %>%
  ungroup() %>%
  mutate(all_subs = rowSums(select(., one_of(c("good_subs", "bad_subs", "ugly_subs")))),
         bad_ugly_subs = rowSums(select(., one_of(c("bad_subs", "ugly_subs"))))) %>%
  gather(variable, value, -c("iso3", "year")) %>%
  spread(year, value) %>%
  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = "iso3") %>%
  mutate(is_WTO = case_when(!is.na(is_WTO) ~ is_WTO,
                            iso3 %in% unique(paste0(territories$sovereign_iso3, "-T")) ~ TRUE,
                            iso3 == "EU" ~ TRUE,
                            TRUE ~ FALSE))

subsidy_lookup <- sumaila_2019_dat_edit %>%
  dplyr::select(iso3, year, type, value) %>%
  mutate(variable = paste0(type, "_subs")) %>%
  dplyr::select(-type) %>%
  group_by(iso3, year, variable) %>%
  summarize(value = sum(value, na.rm = T)) %>%
  spread(year, value) %>%
  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = "iso3") %>%
  mutate(is_WTO = case_when(!is.na(is_WTO) ~ is_WTO,
                            iso3 %in% unique(paste0(territories$sovereign_iso3, "-T")) ~ TRUE,
                            iso3 == "EU" ~ TRUE,
                            TRUE ~ FALSE)) %>%
  bind_rows(subsidy_totals)

# Demographic lookup 
demographic_lookup <- wb_dat_edit %>%
  dplyr::select(-units, -source) %>%
  spread(year, value) %>%
  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = "iso3") %>%
  mutate(is_WTO = case_when(!is.na(is_WTO) ~ is_WTO,
                            iso3 %in% unique(paste0(territories$sovereign_iso3, "-T")) ~ TRUE,
                            iso3 == "EU" ~ TRUE,
                            TRUE ~ FALSE))

# Fishers lookup
fishers_lookup <- fao_fishers_dat_edit %>%
  dplyr::select(-units, -source) %>%
  spread(year, value) %>%
  dplyr::select(-`1995`) %>%
  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = "iso3") %>%
  mutate(is_WTO = case_when(!is.na(is_WTO) ~ is_WTO,
                            iso3 %in% unique(paste0(territories$sovereign_iso3, "-T")) ~ TRUE,
                            iso3 == "EU" ~ TRUE,
                            TRUE ~ FALSE))

# Combine 
cap_tier_lookup <- capture_production_lookup %>%
  bind_rows(landed_value_lookup) %>%
  bind_rows(subsidy_lookup) %>%
  bind_rows(demographic_lookup) %>%
  bind_rows(fishers_lookup)

### 2020-09-04 scripts/07_proposals.Rmd
cap fixes

proposal_choices <- included_proposals$proposal
names(proposal_choices) <- included_proposals$display_name
```
```{r}
# Combined fishery stats dat

>>>>

proposal_choices <- included_proposals$proposal
names(proposal_choices) <- included_proposals$display_name
```

```{r}
# Cap/Tier Data
cap_tier_dat <- read_csv(here::here("app", "data", "USA_cap_tier_tidy.csv")) %>%
  arrange(iso3)

# Data
# 1) Subsidy estimates (Sumaila et al. 2019) ---
subsidy_dat_sumaila_raw <- read_csv("./data/sumaila_et_al_2019_subsidies_tidy.csv") %>%
  arrange(iso3)

# Organize subsidy types as defined by Sumaila et al. (2019) for consistent plotting throughout
subsidy_classification_sumaila <- subsidy_dat_sumaila_raw %>%
  distinct(category, category_name, type, type_name) %>%
  arrange(type)

subsidy_types_sorted_sumaila <- subsidy_classification_sumaila$type
names(subsidy_types_sorted_sumaila) <- subsidy_classification_sumaila$type_name
